Linear Regression Model

Call the data model library and retrieve the ames data from the data model library
```{r}
library(modeldata)
data <- data.frame(ames)
```

Create a simple linear regression model with for or while
```{r}
X <- setdiff(names(data), "Sale_Price")
Y <- data.frame(Variable = character(), R2 = numeric(), stringsAsFactors = FALSE)
for (var in X) {
  formula <- as.formula(paste("Sale_Price ~", var))
  tryCatch({
    model <- lm(formula, data = ames)
    r2 <- summary(model)$adj.r.squared
  }, error = function(e) {
    r2 <- NA
  })
  Y <- rbind(Y, data.frame(Variable = var, R2 = r2))
}
Y
```

Selection of the best model with Adjusted R2
```{r}
BestModel <- Y[which.max(Y$R2), ]
BestModel
```

Create a simple linear regression model using lapply
```{r}
data(ames)
X <- setdiff(names(ames), "Sale_Price")
Y <- lapply(X, function(X) {
  tryCatch({
    model <- lm(Sale_Price ~ ., data = ames[, c("Sale_Price", X)])
    r2 <- summary(model)$adj.r.squared
  }, error = function(e) {
    r2 <- NA
  })
  data.frame(X = X, r2 = r2)
})
Y <- do.call(rbind, Y)
Y
```

Create matrix multiplication with commands %>%
```{r}
matrix1 <- matrix(1:25, nrow = 5, ncol = 5)
matrix2 <- matrix(25:1, nrow = 5, ncol = 5)
Y_r <- matrix1 %*% matrix2
Y_r
```

Create matrix multiplication with the For function
```{r}
Y <- matrix(0, nrow = 5, ncol = 5)
for (i in 1:5) {
  for (j in 1:5) {
    for (k in 1:5) {
      Y[i, j] <- Y[i, j] + matrix1[i, k] * matrix2[k, j]
    }
  }
}
Y
```

Identifikasi apakah model Y sama dengan model Y_r
```{r}
identical(Y, Y_r)
```

